Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-03-31 modeling-volunteer-computing-gecco.tex
Anonymizing again for EvoSoft, addressing some reviewer's comments and questions for @JJ for issue #2

In order to test the volunteer computing environment, a presentation
describing a low cost volunteer computing environment was
created. This presentation was actually delivered in several
conferences\footnote{Names withheld for the double blind review}. During the
conference, it was revealed to the persons attending it that they were participating
in the experiment. The same procedure was used when trying to gather
users in social networks: a description of the container (the
presentation) and disclosure of its purpose. The upper right corner of
the presentation shows the progress of the evolution. It
stops when the solution has been reached.

@@

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/idc-keynote}. These results
will be analyzed in the next section.

>>>>

In order to test the volunteer computing environment, a presentation
describing a low cost volunteer computing environment was
created. This presentation was actually delivered in several
conferences\footnote{Names withheld for the double blind review}. During the %FERGU: TODO JJ, no te olvides de decirme esto. Es la IDC 2014?
conference, it was revealed to the persons attending it that they were participating
in the experiment. The same procedure was used when trying to gather
users in social networks: a description of the container (the
presentation) and disclosure of its purpose. The upper right corner of
the presentation shows the progress of the evolution. It
stops when the solution has been reached.

@@

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{http:\\blind-review} %\url{https://github.com/JJ/idc-keynote}. FERGU: JJ, es este el repo correcto, no?
These results
will be analyzed in the next section.
